The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-11-08 Moving temporal window - HESS/template.tex
Improvement of the CRPSS plots.

>>>>

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
	\caption{Performance score (CRPS, \%) of the analog method on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e. 1961-2008, (yellow) the reduced archive, i.e. 1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibration of the AM parameters with the MTW.}
	\label{fig:plots_CRPSS_2Z}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
	\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analog method with a second level on the moisture variables.}
	\label{fig:plots_CRPSS_2Z-2MI}
\end{figure}
